MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38 - Model Selection

### 2020-04-05 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_SALMON_GRCh38.Rmd
lazy cache for long vectors
compute cor on half of genes to reduce computational load

# Gender
# vcd::mosaic(~ Gender + Dx.Tissue, data = COVARIATES)
```
### Filter genes
Remove genes that have less than 1 cpm counts in at least 50% of samples per Dx.Tissue. Remove genes with percentage GC content
```{r cpmnormalisation}
counts$transcript_id = NULL

@@

### Co-expression distribution
Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(NEW.COUNTS))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

>>>>

# Gender
# vcd::mosaic(~ Gender + Dx.Tissue, data = COVARIATES)
```
### Filter genes
Remove genes that have less than 1 cpm counts in at least 50% of samples per Dx.Tissue. Remove genes with percentage GC content
```{r cpmnormalisation, cache.lazy = FALSE}
counts$transcript_id = NULL

@@

### Co-expression distribution
Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
# Reduce computational load and compute correlation on half of genes
random_sampling <- sample(dim(NEW.COUNTS)[1], size = dim(NEW.COUNTS)[1]/2 , replace = F)
tmp <- NEW.COUNTS[random_sampling,]
cr = cor(t(tmp))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```
